### 2023-11-21 response_to_r1.md

Third, would it be possible to add the learning goals of the EwP module and suggested methods for assessments?

**Response 5**

Each submodule of EwP has a number of learning objectives that appear at the top of each
submodule course webpage. I've added screenshots of these objectives so that readers can see
how the objectives are presented to the students.

As for assessment, in the section of the paper entitled, *Software availability and classroom use*, we describe and make available for download an assignment that we have used for assessment of this material. It covers all aspects of the EwP module.

@@

**Response 1**

I'm definitely not trying to offer EwP as an alternative to Excel. I've taught an Excel based spreadsheet modeling course for over 20 years and have used Excel extensively in both industry as well as in academic settings. I love spreadsheets and have for a long time. But, they do
have their limitations and the better our students are at assessing when a spreadsheet is and is not appropriate, the better off they will be. This is not some novel argument. Excel bashing is rampant in corporate IT and analytics settings. Quite honestly, even Jupyter notebooks have major shortcomings when it comes to productionizing analytical models implemented in Python and I mention this in the paper - and that's why I also make students use an actual IDE to write code in addition to the things we do in notebooks. There's a lot of nuance in knowing how to effectively wield tools like Excel and Python in professional analytics environments. This is a big part of the motivation behind the development of my courses and in writing this paper.

My intent is to provide an interesting way for business students to learn more advanced Python concepts through a very familiar lens of spreadsheet modeling. In addition, I want to expose them to the abilities of Python in automating manipulation of spreadsheets. Now with MS announcing the inclusion of Python within Excel, the complementary nature of these two powerhouse tools will become even more important. To that end, I've modified the beginning of that paragraph as follows:

> Despite numerous calls for, and predictions of, the eradication of spreadsheets from the business world, Excel and other spreadsheets are [alive and well](https://benn.substack.com/p/the-next-billion-programmers). Their flexibility is unparalleled and it is unrealistic to expect them to disappear anytime soon. If anything, the [recent announcement by Microsoft](https://techcommunity.microsoft.com/t5/excel-blog/announcing-python-in-excel-combining-the-power-of-python-and-the/ba-p/3893439)
 that users will be able combine Python scripts with Excel formulas within the same workbook, will likely solidify Excel's place in the analytics space.

### 2023-11-21 python_excel_ite_r1.tex
revision 1 submitted

The PCDA course, like many introductory data science courses, focuses mostly on data wrangling, exploratory data analysis (EDA), and statistical/machine learning based predictive models. In teaching EDA using tools like [ggplot2](https://ggplot2.tidyverse.org/), students are challenged to think about how they would go about trying to use Excel to create some of the plots that are easy to do with R and Python based plotting libraries. There is some limited coverage of using Python to open Excel files and do worksheet manipulation. However, other than a Python based simulation of the Monte Hall 3-door problem, there was no real attempt to do the kind of modeling that is the focus of most spreadsheet based modeling textbooks.

>>>>

The PCDA course, like many introductory data science courses, focuses mostly on data wrangling, exploratory data analysis (EDA), and statistical/machine learning based predictive models. In teaching EDA using tools like \href{https://ggplot2.tidyverse.org/}{ggplot2}, students are challenged to think about how they would go about trying to use Excel to create some of the plots that are easy to do with R and Python based plotting libraries. There is some limited coverage of using Python to open Excel files and do worksheet manipulation. However, other than a Python based simulation of the Monte Hall 3-door problem, there was no real attempt to do the kind of modeling that is the focus of most spreadsheet based modeling textbooks.
